---
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE, 
  warning = FALSE,
  comment = "#>",
  eval = TRUE,
  fig.path = "man/figures/README-"
)
```

# gadgetplots
**Plot gadget3 model output using ggplot2. R package version `r packageVersion("gadgetplots")`**

<!-- badges: start -->
<!-- [![R-CMD-check](https://github.com/gadget-framework/gadgetplots/workflows/R-CMD-check/badge.svg)](https://github.com/gadget-framework/gadgetplots/actions) -->
<!-- badges: end -->

The gadgetplots package produces diagnostics graphics for [gadget3](https://github.com/gadget-framework/gadget3) using [ggplot2](https://ggplot2.tidyverse.org/reference). The package replaces the plotting capabilities of [Rgadget](https://github.com/gadget-framework/rgadget) package which was designed to work with [gadget2](https://github.com/gadget-framework/gadget2). 

## Installation

The gadgetplots is not available on CRAN yet. Use the devtools or remotes packages to install directly from GitHub:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("gadget-framework/gadgetplots")
```

## Usage

See the [**function reference**](https://gadget-framework.github.io/gadgetplots/reference/index.html) for a detailed list of functions and documentation on how to use them. 

The [`make_html()`](https://gadget-framework.github.io/gadgetplots/reference/make_html.html) function generates a [single html file](https://gadget-framework.github.io/gadgetplots/articles/make_html_output.html) out of [`gadgetutils::g3_fit()`](https://rdrr.io/github/gadget-framework/gadgetutils/man/g3_fit.html) output that contains key model diagnostics. Further, the package produces plots in four categories:

1) `plot_*()` functions plot gadget model **output** generated using [`gadgetutils::g3_fit()`](https://rdrr.io/github/gadget-framework/gadgetutils/man/g3_fit.html). These functions have a generic shorthand, the [`plot()`](https://gadget-framework.github.io/gadgetplots/reference/plot.gadget.fit.html), with `param` argument specifying the type of plot.

2) `dplot_*()` functions plot gadget model **input data** generated using [mfdb](https://github.com/gadget-framework/mfdb), [`gadgetutils::g3_data()`](https://rdrr.io/github/gadget-framework/gadgetutils/man/g3_data.html) or [`gadgetutils::add_g3_attributes()`](https://rdrr.io/github/gadget-framework/gadgetutils/man/add_g3_attributes.html) functions.

3) the `g3d_plot()` function plots **data directly** from a gadget model object.

4) `g3plot_*` functions plot gadget **suitability (selectivity) functions**.

## Found a bug or desire a feature?

The package is under an active development together with gadget3 framework. Please report bugs and write feature requests under [Issues](https://github.com/gadget-framework/gadgetplots/issues).




