---
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE, 
  warning = FALSE,
  comment = "#>",
  eval = TRUE,
  fig.path = "man/figures/README-"
)
```

# gadgetplots
**Plot gadget3 model output using ggplot2. R package version `r packageVersion("gadgetplots")`**

<!-- badges: start -->
[![R-CMD-check](https://github.com/gadget-framework/gadgetplots/workflows/R-CMD-check/badge.svg)](https://github.com/gadget-framework/gadgetplots/actions)
<!-- badges: end -->

The gadgetplots package produces diagnostics graphics for [gadget3](https://github.com/gadget-framework/gadget3) using [ggplot2](https://ggplot2.tidyverse.org/reference). The package replaces the plotting capabilities of [Rgadget](https://github.com/gadget-framework/rgadget) package which was designed to work with [gadget2](https://github.com/gadget-framework/gadget2). 

## Installation

The gadgetplots is not available on CRAN yet. Use the devtools or remotes packages to install directly from GitHub:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("gadget-framework/gadgetplots")
```

## Overview of plots

The package produces plots in four categories: 1) `plot_*()` functions plot gadget model output generated using the `gadgetutils::g3_fit()` function; 2) `dplot_*()` functions plot gadget model input data generated using  [mfdb](https://github.com/gadget-framework/mfdb), `gadgetutils::g3_data()` or `gadgetutils::add_g3_attributes()` functions; 3) the `g3d_plot()` function plots data directly from a gadget model object; and 4) `g3plot_*` functions plot gadget suitability (selectivity) functions. The `plot_*()` functions have a generic shorthand, the `plot()` with `param` argument specifying the type of plot.

Further, it is possible to use the `make_html()` function produce html overviews of gadget models and the `gadget_plots()` function to print multiple central `plot_*`s to png files. 

Under are generic examples of available plots using the `r packageVersion("gadgetplots")` version of gadgetplot package. These may be outdated. 

### `plot_*` for `g3_fit` output

Load example data to demonstrate the plots:

```{r}
library(gadgetplots)
data(fit) # Note that we'll need a better example dataset
```

#### Annual (ICES) plot

```{r}
plot_annual(fit) # synonym: plot(fit)
```

#### Stock biomass and abundance

```{r}
plot_biomass(fit, total = TRUE) # synonym: plot(fit, "total")
```

```{r}
plot_biomass(fit, geom_area = TRUE) # synonym: plot(fit, "biomass", geom_area = TRUE)
```

```{r}
plot_biomass(fit, biomass = FALSE) # synonym: plot(fit, "abundance")
```

#### Spawning stock

Currently requires definition of spawning stock among stocks in the gadget model (uses a reasonable guess: `grep("fem.*mat")`). Defining spawning stock based on length or age from the model is also possible, but needs to be implemented.

```{r}
plot_ssb(fit) # synonym: plot(fit, "ssb")
```

#### Recruitment

```{r}
plot_rec(fit) # synonym: plot(fit, "rec")
```

#### Fishing mortality (F)

```{r}
plot_f(fit) # synonym: plot(fit, "f")
```

#### Modeled catches and harvest rate

```{r}
plot_catch(fit, type = "stock") # synonym: plot(fit, "catch")
```

```{r}
plot_catch(fit, type = "fleet") # synonym: plot(fit, "fleet")
```

```{r}
plot_catch(fit, type = "hr") # synonym: plot(fit, "hr")
```

#### Survey indices

```{r}
plot_si(fit) # synonym: plot(fit, "si")
```

#### Catch distribution

The function typically produces a list of plots. Here only one to save space

```{r}
plot_catchdist(fit, name = "EggaN_ldist") # synonym: plot(fit, "catchdist")
```

#### Stock distribution

```{r}
plot_stockdist(fit) # synonym: plot(fit, "stockdist")
```

#### Stock composition

```{r}
plot_stockdist(fit, type = "stock_composition") # synonym: plot(fit, "stockcomp")
```


#### Suitability (fleet selection)

```{r}
plot_suitability(fit) # synonym: plot(fit, "suitability")
```

#### Average length by age (growth)

```{r}
plot_growth(fit) # synonym: plot(fit, "growth")
```

#### Age-length fit

Returns as many plots as there are separate age-length data sources. Only one plotted here to save space.

```{r}
plot_agelength(fit, name = "EggaN_aldist_female") # synonym: plot(fit, "agelength")
```

#### Age composition

```{r}
plot_agecomp(fit) # synonym: plot(fit, "agecomp"), also "stock.std" works
```

#### Residuals

```{r}
plot_resid(fit) # synonym: plot(fit, "resid")
```

#### Likelihood

```{r}
plot_likelihood(fit) # synonym: plot(fit, "likelihood")
```

```{r}
plot_likelihood(fit, type = "weighted") # synonym: plot(fit, "weighted")
```

```{r}
plot_likelihood(fit, type = "sums") # synonym: plot(fit, "sums")
```

#### Parameters

Parameter component weights:

```{r}
plot_weight(fit) # synonym: plot(fit, "weight")
```

```{r, fig.height=15}
# plot_param(fit) # synonym: plot(fit, "param") # need to add bounds to g3_fit
```

### Quickly plot central diagnostics

#### HTML files

The `gadget_plot()` produces a range of diagnostic plots into a folder specified by the `path` argument. You may also use the `file_type = "html"` argument to save these plots into a single html file. There is also the `make_html()` to produce the html file directly without a wrapper function. 

#### Png files


### `dplot_*` for gadget input data


### `g3d_plot` for gadget model objects


### `g3plot_*` for suitability functions



## Found a bug or desire a feature?

The package is under an active development together with gadget3 framework. Please report bugs and write feature requests under [Issues](https://github.com/gadget-framework/gadgetplots/issues).




